Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-23 manuscript.Rmd
move zenodo section

To summarize, researchers need to write three functions, `planned_analysis()`, `simulate_data()`, and `report_analysis()` and embed these into a manuscript that serves as a preregistration.
After they gathered the actual data, they can replace the simulated data, render the dynamic manuscript (therefore run `planned_analysis()` on the actual data), and write the discussion.

@@

# Preregistration as Code: Tutorial

>>>>

### Turning a Dynamic Document into a Preregistration

To summarize, researchers need to write three functions, `planned_analysis()`, `simulate_data()`, and `report_analysis()` and embed these into a manuscript that serves as a preregistration in an uneditable online repository.
After they gathered the actual data, they can replace the simulated data, render the dynamic manuscript (therefore run `planned_analysis()` on the actual data), and write the discussion.

@@

## Preregistration as Code: Tutorial
